### 2017-03-23 thesis/misc/glossary.tex
tmp commit
Finished editing methods
Finished editing results1

% TODO: make sure you get a proper definitions for all of these glossary terms

@@

@@

@@

@@

@@

>>>>

@@

\newglossaryentry{immunoediting}{
	name=Immunoediting,
	text=immunoediting,
	description={Process where the immune system successfully eliminates the highly immunogenic cancer cells during surveillance, but fails to eliminate the weakly immunogenic cells}
}

@@

\newglossaryentry{carcinogen}{
	name=Carcinogen,
	text=carcinogen,
	plural=carcinogens,
	description={A substance capable of causing cancer}
}

\newglossaryentry{passenger}{
	name=Passanger mutation,
	text=passanger,
	description={Mutations that have neither a selective advantage nor contribute to tumour progression}
}

\newglossaryentry{driver}{
	name=Driver mutation,
	text=driver,
	description={Mutations that helps tumorigenesis and its subsequent progression}
}

\newglossaryentry{somatic}{
	name=Somatic mutation,
	text=somatic mutation,
	plural=somatic mutations,
	description={Mutations that are acquried by the cell over the course of the lifetime of an individual}
}

\newglossaryentry{germline}{
	name=Germline mutation,
	text=germline mutation,
	plural=germline mutations,
	description={Mutations that are passed on from the parents}
}

\newglossaryentry{stability}{
	name=Stability gene,
	text=stability gene,
	plural=stability genes,
	description={Genes that are involved in \acrshort{dna} repair mechanisms}
}

\newglossaryentry{allele}{
	name=Allele,
	text=allele,
	plural=alleles,
	description={Variant form of a given gene}
}

\newglossaryentry{suppressor}{
	name=Tumour suppressor gene,
	text=tumour suppressor,
	description={Genes that prevent or ``decelerate'' the process of tumorigenesis and/or tumour progression}
}

\newglossaryentry{oncogene}{
	name=Oncogene,
	text=oncogene,
	plural=oncogenes,
	description={Genes that promote or ``accelerate'' the process of tumorigenesis and/or tumour progression}
}

@@

\newacronym{aic}{AIC}{Akaike Information Criterion}

@@

\newacronym{gsea}{GSEA}{Gene Set Enrichment Analysis}

@@

\newacronym{rna}{RNA}{ribonucleic acid}
